Simulation_Study

### 2022-03-13 Simulation_Study.Rmd
Tests for Different Block Lengths

>>>>

for(n in c(1, 8, 27, 64, 125, 216, 343, 512, 729, 1000, 1331, 1728, 2197, 2744, 3375))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.1, 0.1, n**(1/3), m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.1),
     sigma = c(0.1),
     l = c(n**(1/3)),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

ggplot(test_reshaped, aes(x, y, col = group)) +  scale_x_sqrt() + geom_point()

for(n in c(1, 16, 81, 256, 625, 1296, 2401, 4096))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.1, 0.1, n**(1/4), m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.1),
     sigma = c(0.1),
     l = c(n**(1/4)),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

ggplot(test_reshaped, aes(x, y, col = group)) +  scale_x_sqrt() + geom_point()

for(n in c(1, 32, 243, 1024, 3125, 7776))
{
  for(i in 1:3)
  {
    sim <- replicate(100, do1rep(n, 0.1, 0.1, n**(1/5), m1))
    m <- my_summary(sim)
    tobind.data <- data.frame(
     n = c(n),
     ar = c(0.1),
     sigma = c(0.1),
     l = c(n**(1/5)),
     mean = c(m[1]), 
     nm_se = c(m[2]),
     nm_lower = c(m[3]), 
     nm_upper = c(m[4]),
     nm_success = c(m[5]),
     mv_se = c(m[6]),
     mv_lower = c(m[7]), 
     mv_upper = c(m[8]),
     mv_success = c(m[9]),
     true_se = c(m[10]),
     nm_diff = c(m[11]),
     mv_diff = c(m[12]),
     nm_percent_diff = c(m[13]),
     mv_percent_diff = c(m[14])
    )
    test.data = rbind(test.data, tobind.data)
  }
}

ggplot(test_reshaped, aes(x, y, col = group)) +  scale_x_sqrt() + geom_point()
